Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-21 paper.Rmd
first stab into different levels

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)

@@

#Here I will assign only one month - "202105". If you want to include a full year, just assign year to "2021" or "2020". It works.
year <- "202105"
file_names <- list_apt_files(.year = year)
open_sky <- map_dfr(file_names, read_csv)

@@

```{r}
#quick peek
base_dataset
#
#
#
#NOW IT'S TIME TO LOOP TO OTHER MONTHS AND BIND THEM ALL!
#
#
#

#quick first look
temp1 <- base_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n()) %>% mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused")

temp1 %>% ggplot(aes(x = DATE)) +
  geom_line(aes(y = (FLIGHTS), color = ROUTE))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(stats)
library(zoo)
```

@@

#Here I will assign only one month - "202105". If you want to include a full year, just assign year to "2021" or "2020". It works.
year <- "2021"
file_names <- list_apt_files(.year = year)
open_sky <- map_dfr(file_names, read_csv)

@@

```{r}
#quick peek
base_dataset
#
#
#
#NOW IT'S TIME TO LOOP TO OTHER MONTHS AND BIND THEM ALL!
#
#
#
```

```{r}
#quick first look
temp1 <- base_dataset %>% group_by(DATE, ADEP_REG, ADES_REG) %>% summarize(FLIGHTS = n(), .groups = "drop") %>%
  filter(ADEP_REG %in% c("BR", "EU"), ADES_REG  %in% c("BR", "EU")) %>%
  mutate(ROUTE = paste(ADEP_REG, ADES_REG, sep = "-"), .keep = "unused", .before = "FLIGHTS") %>%
  pivot_wider(names_from = ROUTE, values_from = FLIGHTS) 
temp1

#First stab at different levels of traffic

n <- 0.5
temp1 %>% ggplot(aes(x = DATE)) +
  geom_point(aes(y = `EU-EU`, color = `EU-EU` > quantile(`EU-EU`[month(DATE) %in% 1:2], probs = n)), shape = 4) +
  geom_point(aes(y = `BR-BR`, color = `BR-BR` > quantile(`BR-BR`[month(DATE) %in% 1:2], probs = n)), shape = 1) +
  labs(y  = "Flights") + 
  theme(legend.position = "bottom")

#Normalized by the median of the last 3 months
temp2 <- temp1 %>% pivot_longer(cols = 2:5, names_to = "ROUTE", values_to = "FLIGHTS") %>% group_by(ROUTE) %>% mutate(MOVING_MEDIAN = quantile(FLIGHTS[month(DATE) %in% month(last(DATE))-1:month(last(DATE))], probs = 0.5), NORM_FLTS = FLIGHTS/MOVING_MEDIAN)
temp2

temp2 %>% ggplot(aes(x = DATE)) +
  geom_line(aes(y = NORM_FLTS, color = ROUTE)) +
  theme_minimal()
```

```{r}
